---
title: "Creating the Water Chemistry Dataframe"
output:
 html_document:
    df_print: paged
    code_folding: hide
    toc: TRUE
    toc_depth: 4
    toc_float: true
    theme: journal
    highlight: zenburn
    smart: false

---

```{r 0.0 Libraries , echo=FALSE, results=FALSE}
#*********************************
##Libraries
#********************************* 
library(shiny)
library(tidyverse)
library(stringr)
library(readxl)
library(readr)
library(tidyr)
library(yaml)
library(dplyr)
library(data.table)
library(lubridate)
library(violinmplot)
library(vioplot)
library(yarrr)
library(datapasta)
library(reprex)
library(miniUI)
library(gridExtra)
library(wql)
```



# 1. Setting the Working Directory
1.0
Look for all files inside the Water Chemistry folder of the "06. MOATs replication verification" folder
```{r 1.0 Setting Working Directory, ECHO= FALSE, message=FALSE, warning=FALSE}
#*********************************
## 1.) Set working directory
#*********************************
knitr::opts_chunk$set(echo = TRUE)

knitr::opts_knit$set(root.dir =
                       "/Users/katherinerovinski/GIT/NWFSC.MUK_KRL_SMR2019_WinterStormEvent")
```



#### 1.1 Initial Working Directoy
Inside the working directory (folder) is 1 CSV files generated after combining 13CSV logs representing 24second observations. These CSV files were created using the moats graph app



#### 1.1.2 Link to Generating App
[Link to moats.Graph.app](http://github.com/pmcelhany/moatsGraphs.git)
Moving average window (nObs) set to 4. 



#### 1.1.3 Protocol with app
Every 17th observations was selected, the observations were 24second apart. 



#### 1.1.4 App data for 13 MOATS
1 CSVs per moats: M01, M02, M03, M04, M05, M06, M07, M08, M09, M10, M11, M12, M13. Files are also available on the OA Google drive. [OA Drive for MOATS data](https://drive.google.com/open?id=13a2hk1a9I9gRIgf2Xyl1dSYDf5vnyYvs)



### 1.2 Subsampling
For speed and ease of computations the dataframe was extermely subsampled. 
Instead of the standard "n17" used in the aquarium temperature investigation, this document subsampled at "n333".



#### 1.2.1 Subsampling explained by observations
All observations (per the 13 MOATS logs)
[1] 1137880   7 (6 seconds)
Number of observations after subsampling every 17th response/observation
[1] 66934     7 (24 seconds)
Number of observations after the super-subsampling, every 333rd observation
[1] 3417      7 (~30minutes) ***this won't detail the ramp



#### 1.2.2 Subsampling Determination
To examine the Day to Night ramp (D2Nramp) researcher used n17 subsampling group



# 2.0) Calling and Reading in dml
```{r 2.0 Calling and Reading in dml, ECHO= FALSE, message=FALSE, warning=FALSE, }
#*********************************
## 2. Calling & Reading in " dml " 
#*********************************

# Super Speedy subsampled data
dml <- read.csv(file = "M01thruM13moatslog_n17.csv", stringsAsFactors = FALSE)
dim(dml)

```



# 3.0) Reformatting variables/vectors (Factors)
Changing MOATs to Factors for the 13 different MOATs- these will be the discrete units for follow analysis
```{r Reformatting variables/vectors (Factors), ECHO= FALSE, message=FALSE, warning=FALSE}
#*********************************
## 3. Reformatting variables/vectors (Factors) 
#*********************************

## 3.3 Changing variables | 
dml$moats <- factor(dml$moats)
# Checking the names of the different levels
levels(dml$moats)
##checking the dataset, dimensions
dim(dml)
```



# 4.0) Creating dateTime objects  
Changes to the format of dates and times for observations
```{r 4.0 establish the date time object of the CSV, ECHO= FALSE, message=FALSE, warning=FALSE}
#*********************************
## 4.) Creating dateTime objects  
#*********************************

# 4.0 establish the date time object of the CSV |
dml$dateTime <- as.POSIXct(dml$dateTime, format="%Y-%m-%d %H:%M:%OS")
ReferenceTime <- as.POSIXct("2019-09-20 23:59:00")
class(ReferenceTime)

# QA check
dim(dml)
```



# 5.0) Creating Treatment Variables  
#### 5.1 Three Treatments
Three treatments of this studies are identified as 
* "current" for the Current Conditions Treatment
* "hightemperature" for the High Temperature Conditions Treatment
* "allchange" for the All Change Conditions Treatment which incorporated both the high temperature conditions of the "hightemperature" treatment along with exposure to lower aquarium pH.   
```{r 5.1 Identifying treatments by moats, ECHO= FALSE, message=FALSE, warning=FALSE}
#*********************************
## 5.) Creating Treatment Variables  
#*********************************

## 5.1 Identifying treatments by moats 
## establishing treatments
dml$treatment <- ""
dml$treatment[dml$moats == "M07" | dml$moats== "M10" | dml$moats== "M12"] <- "current"
dml$treatment[dml$moats == "M01"| dml$moats== "M06"] <- "hightemperature"
dml$treatment[dml$moats == "M02"| dml$moats== "M08" | dml$moats== "M13"] <- "allchange"
dml$treatment[dml$moats == "M03"| dml$moats == "M04" | dml$moats == "M05" | dml$moats== "M11"] <- "broken_and_ambientbroken"
#verify that this new column has been created
names(dml)
#results should include:
#[1] "moats"        "dateTime"     "aTemperature" "sTemperature" "pH"          
#[6] "DO"           "salinity"     "treatment"  

# QA check
dim(dml)


```



#### 5.1.1 Ambient Treatment
Those MOATS aquarium systems that did not reach desired/programed conditions were deemed the "ambient" treatment. No temperature, DO, or pH conditions were programmed or alarmed. Flow control was governed by a solenoid valve to acheive flow/no-flow, day/night periods. 

MOATS inside the "Ambient" treatment included MOATs 04 and MOATs 05 both were shown to have faulty thermisters. 
Recorded conditions of what the animals experienced can't be guaranteed/confirmed. 
Without a record of aquarium settings MOATs 04 and MOAT 05 data was not included. 



# 6.) Creating Night and Day Periods 
#### 6.1 Narrative (Overall)
Creating a day and night variables 
Day and night periods will only refer to time under treatment as a way to exclude the acclimation period.
Day and night changed at about ~ 1230 on 05OCT19 
Treatment start date considered to begin Monday 23SEP19 at 1200pm
Krill Night Starts 1200 (~1230*) and ends 2100
Krill Days Starts 2101 and ends 1159 (~1229*) 
Interval 1 start 1200 23SEP19, end 1229 05OCT19
Interval 2 start 1230 05OCT19, end 2100 30OCT19



#### 6.2 New Column, New Variable in dml 
```{r 6.2 New Column, New Variable in dml}
## 6.2 New Column, New Variable in dml
#creating a new column, new variable "period"
dml$period <- ""
```



#### 6.3 Disassembling dateTime to create 2 new variables
```{r 6.3 Disassembling dateTime to create 2 new variables}
## 6.3 Disassembling dateTime to create 2 new variables
# Create new split date and time columns
dml$ObservationDate <- as.Date(dml$dateTime)
dml$ObservationTime <- format(as.POSIXct(dml$dateTime) ,format = "%H:%M:%S")
```



#### 6.4 Narrative about Intervals 
Interval 1
Interval Date Start  "2019-09-23"
Interval Date End    "2019-10-05"
Day Start Time       "21:01:00"
Day End Time         "11:29:00"
Night Start Time     "12:00:00"
Night End Time       "21:00:00"
DaytoNight Ramp(D2N) "11:30:00"
start
DaytoNight Ramp(D2N) "11:59:00"
stop
Other Time


Interval 2
Interval Date Start  "2019-10-05"
Interval Date End    "2019-10-30"
Day Start Time       "21:01:00"
Day End Time         "12:29:00"
Night Start Time     "12:30:00"
Night End Time       "21:00:00"
Other Time



#### 6.5 Period Assignments
```{r 6.5 Day / Night Assignments,  ECHO= FALSE, message=FALSE, warning=FALSE}
## 6.5 Day / Night Assignments 
# Using the "case_when" function in the tidyverse in the place of a loop
 
dml <- dml %>% mutate(period=case_when(
  (ObservationDate >= "2019-09-23") 
  & (ObservationDate <="2019-10-05") 
  & (ObservationTime >= "12:00:00") 
  & (ObservationTime <="21:00:00") ~"night",
  
  (ObservationDate >= "2019-10-05")
  & (ObservationDate <= "2019-10-30")
  & (ObservationTime >= "12:31:00") 
  & (ObservationTime <="21:00:00") ~"night",
  
  (ObservationDate >= "2019-09-23") 
  & (ObservationDate <="2019-10-05")
  & ((ObservationTime >= "21:01:00") 
     | (ObservationTime <="11:29:00")) ~"day",
  
  (ObservationDate >= "2019-10-05")
  & (ObservationDate <= "2019-10-30")
  & ((ObservationTime >= "21:01:00")
     | (ObservationTime <= "12:01:00")) ~"day",
  
  (ObservationDate >= "2019-09-23") 
  & (ObservationDate <="2019-10-05")
  & ((ObservationTime >= "11:30:00") 
     | (ObservationTime <="12:00:00")) ~"D2Nramp",
  
  (ObservationDate >= "2019-10-05")
  & (ObservationDate <= "2019-10-30")
  & ((ObservationTime >= "12:01:00")
     | (ObservationTime <= "12:30:00")) ~"D2Nramp",

  
  TRUE ~"other"
)

) 
```



#### 6.5.1 Quick Check on Period Generation
```{r 6.5.1 aTemperature Time Series Plots to Invesitgate Different Intervals}
#Quick check to see if periods were created

period.intervals <- ggplot(dml, aes(x=dateTime, y=aTemperature)) +
  geom_point(aes(colour=period, point=))   +
  ggtitle("aTemperature Time Series Plots to Invesitgate Different Intervals") +
  ylim (5.0, 15.00)

period.intervals
```



#### 6.5.1 Quick Check on Day to Night Ramp Verification
The ramp verification will be important to dissolved oxygen verification
Dissolved oxygen not yet shown. 
Recorded dissolved oxygen needs to be corrected with observed salinity. 
The following 2 plots are only present to visualize the different periods across treatments



#### 6.5.1a Quick Check on Day to Night Ramp Verification
```{r  6.5.1a Quick Check on Day to Night Ramp Verification}
ggplot(subset(dml, 
               period %in% ("D2Nramp")), 
        aes(x=dateTime, y=aTemperature)) + 
   geom_point(aes(colour=treatment, point=)) +
   ylim (5.0, 15.00) + 
   ggtitle("aTemperature Values, All MOATs, During Day to Night Ramp Period")

```



#### 6.5.1b Quick Check on Day to Night Ramp Verification
```{r 6.5.1b Quick Check on Day to Night Ramp Verification}

ggplot(subset(dml[dml$treatment == "allchange", ], 
             period %in% ("D2Nramp")), 
       aes(x=dateTime, y=aTemperature)) + 
  geom_point(aes(colour=moats, point=)) +
  ggtitle("Aquarium Temperatures, All Change, During Ramp Period")

```



#### 6.6 Removing the Acclimation Period 
The acclimation and the time after animals were removed from the system was designated other
```{r 6.6 Removing the Acclimation Period }

# Removing "other" period from day and night 
# not including acclimation period in this investigation

H2Ochemdf <- dml %>% filter(period != "other")
```
#### Water Chemistry Dataframe Created "H2Ochemdf"



# 7.) Bringing in Salinity   
```{r 7.0 Bringing in Salinity }
all_salinity <- read.csv(file = "KRL19_salinityreadings_all.csv", stringsAsFactors = FALSE)
all_salinity$PSU_ObsDate <- ""

all_salinity$Date <- as.POSIXct(all_salinity$Date, format= "%m/%d/%y")
all_salinity$PSU_ObsDate <- as.Date(all_salinity$Date)
```



# 8.0) Creating Corrected Salinity Value   
#### 8.1) Narrative: Creating Corrected Salinity Value from Point Measurments 
Notes from the 2020.05.29 office hours 
creating 4 new variables in Water Chemistry Dataframe
create a vector 181845  for the large n17 file
create a vector 9283 observations long for the sub-sub sample n333 file
logical vectors- boolean answers to those three below conditions
1 - the measurement per moats per day - MOATs and Data are both available
2 - the measurement (averaged across moats) - group by / summarize tools
3- (data gapped situation- no value matches) take the previous daily average based on observation  - lag? 
previous line on a dataframe ... dplyr tool ... 
 https://dplyr.tidyverse.org/reference/lead-lag.html
4 - "the winning value" case_when #corrected conductivity value
```{r 8.1) Creating Corrected Salinity Value}
# Salinity Values 
H2Ochemdf$PSUperMOATs <- ""
H2Ochemdf$PSUavgDaily <- ""
H2Ochemdf$PSUprevObs <- ""
H2Ochemdf$assumed_PSU <- ""
H2Ochemdf$Final_PSU <- ""
```



#### 8.1a Plots (timeseries verification)
#### Simple Plot 8.1.1
```{r 8.1.1 Plots (timeseries verification)}
# 8.1 Plots (timeseries verification)

p <- ggplot(H2Ochemdf, aes(x=ObservationDate, y=salinity))+
             geom_line() + 
             ylim (30.05, 27.00) 
p

```



#### Simple Plot 8.1.2 Salinity Values all Treatments, All MOATs, During Night Period
```{r 8.1.2 Salinity Values all Treatments, All MOATs, During Night Period}
ggplot(subset(H2Ochemdf, 
               period %in% ("night")), 
        aes(x=ObservationDate, y=salinity)) + 
        geom_point(aes(colour=period, point=)) +
        ggtitle("Salinity Constants all Treatments, All MOATs, During Night Period")
```



#### Simple Plot 8.1.3
```{r 8.1.3 Salinity Constants all Treatments, All MOATs, During Night Period }

ggplot(subset(H2Ochemdf, 
               period %in% ("night")), 
        aes(x=ObservationDate, y=salinity)) + 
        geom_point(aes(colour=moats, point=)) +
        ggtitle("Salinity Constants all Treatments, All MOATs, During Night Period")
```



#### 8.1.4 Salinity Constants, MOATs 01, During Night Period
```{r 8.1.4 Salinity Constants all Treatments, All MOATs, During Night Period}
ggplot(subset(H2Ochemdf[H2Ochemdf$moats == "M01", ], 
               period %in% ("day")), 
        aes(x=dateTime, y=salinity)) + 
   geom_point(aes(colour=moats, point=)) +
   ggtitle("Salinity Constant, MOATs 01, During Night Period")
```



#### 8.2 Practical Salinity Units - Measurements Per Moats per Day
These observations consist of salinity measurements taken per MOATS per day.
The observation were recorded per MOATS per day as the researcher took point measurements from the aquarium box while doing DO measurements. 
```{r 8.2 Practical Salinity Units - Measurements Per Moats per Day}
# Manual Readings
# Per MOAT measurement
H2Ochemdf$PSUperMOATs <- all_salinity$salinity[match
                                               (paste
                                                 (H2Ochemdf$ObservationDate,
                                                   H2Ochemdf$moats), 
                                                 paste
                                                 (all_salinity$PSU_ObsDate, 
                                                   all_salinity$moats))]
```



#### 8.3 Practical Salinity Units - Daily Avg Measurement 
Manual records sometimes have holes
Monday through Friday averages were recorded with greater fidelity than weekend averages. 
```{r 8.3 Practical Salinity Units - Daily Avg Measurement}
# All MOATs daily
H2Ochemdf$PSUavgDaily <- all_salinity$salinity[match
                                               (paste
                                                 (H2Ochemdf$ObservationDate,'All'), 
                                                 paste
                                                 (all_salinity$PSU_ObsDate, 
                                                   all_salinity$moats), 
                                                 nomatch = NA_character_)]
```



#### 8.4 Practical Salinity Units - Previous Daily Avg Measurement 
DO point measurements occured weekly. 
Salinity averages were typically recorded every day, Monday- Friday.
Some DO measurements were a week apart. 
The previous daily average was thought to be a better reflection than the last per Day, per MOATs salinity measurement.



#### 8.4.1 Last Observation Carried Forward Function
(Description)
Generic function for replacing each NA with the most recent non-NA prior to it.
This function was used to cover those gaps that occured most weekends.
```{r 8.4.1 Practical Salinity Units - Previous Daily Avg Measurement}
# Previous All MOATs daily
H2Ochemdf$PSUprevObs <- na.locf(H2Ochemdf$PSUavgDaily, na.rm = FALSE)
```



#### 8.5 Practical Salinity Units - Assumed Salinity Value 
Before the start of the study, a salinity of 28.8PSU was observed the week prior to the study's start
```{r 8.5 Practical Salinity Units - Assumed Salinity Value}
 
H2Ochemdf$assumed_PSU <- 28.8

```



#### 8.6 Practical Salinity Units - Final Salinity Value 
cycling between different salinity measurements required moving between character based and numeric based functions.
```{r 8.6a Review of Vectors, Creating Final_PSU value}

# 8.6a Review of Vectors
# Review of the three different salinity values
# H2Ochemdf$PSUperMOATs       measurement
#           PSUperMOATs       per MOATS per Day

## PSUperMOATs

# H2Ochemdf$PSUprevObs        Daily Average
#           PSUavgDaily       measurment across MOATs

## PSUavgDaily 

# H2Ochemdf$PSUprevObs        Previous Daily 
#           PSUprevObs        Average to cover those gaps

## PSUprevObs 

# Sailinity Assumption        28.8
#           Dates w/o         Dates without measurment 23~30SEP20
28.8


# Final Salinity
H2Ochemdf$Final_PSU <- 0.0

# H2Ochemdf$PSUperMOATs <- ""
# H2Ochemdf$PSUavgDaily <- ""
# H2Ochemdf$PSUprevObs <- ""
# H2Ochemdf$assumed_PSU <- ""

H2Ochemdf$Final_PSU <- as.numeric(case_when(
  H2Ochemdf$PSUperMOATs != 'NA' ~ H2Ochemdf$PSUperMOATs,
  H2Ochemdf$PSUavgDaily != 'NA' ~ H2Ochemdf$PSUavgDaily,
  H2Ochemdf$PSUprevObs != 'NA' ~ H2Ochemdf$PSUprevObs,
  TRUE ~ as.character(H2Ochemdf$assumed_PSU),
))

```



#### 8.7 Exmaple of Salinity Corrections (table/Tribble)
```{r 8.7 Exmaple of Salinity Corrections (table/Tribble)}
# placeholder for a knit table

```



#### 8.7A Variation in Salinity Across all Replicates
```{r 8.7A Variation in Salinity Across all Replicates}
FinalSalinity.by.Day <- ggplot(H2Ochemdf, 
                               aes(x=ObservationDate, y=Final_PSU))+
                                geom_point(aes(colour=moats, point=)) +
                                  ggtitle("Salinity Values, all MOATS per Day ")
FinalSalinity.by.Day
```



#### 8.8 Variation in Salinity- All Change Treatment
```{r 8.8 Variation in Salinity- All Change Treatment}
plot8.8 <- ggplot(subset(H2Ochemdf, 
               treatment %in% ("allchange")), 
        aes(x=ObservationDate, y=Final_PSU)) + 
        geom_point(aes(colour=moats, point=)) +
        ggtitle("Salinity Variation Across All Change Treatment Replicates")
plot8.8
```



#### 8.9 Variation in Salinity- High Temperature Conditions Treatment
```{r 8.9 Variation in Salinity- High Temperature Conditions Treatment}
plot8.9 <- ggplot(subset(H2Ochemdf, 
               treatment %in% ("hightemperature")), 
        aes(x=ObservationDate, y=Final_PSU)) + 
        geom_point(aes(colour=moats, point=)) +
        ggtitle("Salinity Variation Across High Temperature Conditions Treatment Replicates")
plot8.9
```



#### 8.10 Variation in Salinity- Current Conditions Treatment
```{r  8.10 Variation in Salinity- Current Conditions Treatment}
plot8.10 <- ggplot(subset(H2Ochemdf, 
               treatment %in% ("current")), 
        aes(x=ObservationDate, y=Final_PSU)) + 
        geom_point(aes(colour=moats, point=)) +
        ggtitle("Salinity Variation Across Current Conditions Treatment Replicates")
plot8.10
```



# 9.) Creating Percent Dissoved Oxy Value 
The Library wql is required for the following chunk 
The package name stands for ``water quality'' and reflects the # original focus on time series data for physical and chemical # properties of water, as well as the biota. Intended for # programs that sample approximately monthly, quarterly or # annually at discrete stations, a feature of many legacy data # sets. Most of the functions should be useful for analysis of # similar-frequency time series
regardless of the subject # matter.



#### 9.1) Creating Percent Dissolved Oxy Value - creating variables  
```{r 9.1 Creating Percent Dissolved Oxygen Value,  ECHO= FALSE, message=FALSE, warning=FALSE}

#assumption with the 28.8 standard salinity reading
H2Ochemdf$percentDOassumpt <- ""
H2Ochemdf$percentDOassumpt <- as.numeric(H2Ochemdf$percentDOassumpt)

H2Ochemdf$assumedSatDOmg <- ""
H2Ochemdf$assumedSatDOmg <- as.numeric(H2Ochemdf$assumedSatDOmg)

# the percent DO
H2Ochemdf$percentDO <- "" 
H2Ochemdf$percentDO <- as.numeric(H2Ochemdf$percentDO)


# Observed / Measured Salinity readings informed answers
H2Ochemdf$obseveredSatDOmg <- "" 
H2Ochemdf$obseveredSatDOmg <- as.numeric(H2Ochemdf$obseveredSatDOmg)


H2Ochemdf$actualDOmg <- ""
H2Ochemdf$actualDOmg <- as.numeric(H2Ochemdf$actualDOmg)

# Review of Values
H2Ochemdf$percentDOassumpt
H2Ochemdf$assumedSatDOmg
H2Ochemdf$percentDO
H2Ochemdf$obseveredSatDOmg
H2Ochemdf$actualDOmg


```



#### 9.2) Creating Percent Dissoved Oxy Value - assumed DO saturation variable creation
```{r 9.2) Creating Percent Dissoved Oxy Value - assumed DO saturation variable creation}

# saturated mg/L DO at obseved temperature and assumed salinity
# the oxySol() function is form the wql package
H2Ochemdf$assumedSatDOmg <- oxySol(H2Ochemdf$sTemperature, 
                                   H2Ochemdf$assumed_PSU)


SatDOplot <- ggplot(H2Ochemdf, aes(x=ObservationDate, 
                                   y=assumedSatDOmg))+
  geom_point(aes(colour=treatment, point=)) +
  ggtitle("Assumed Saturation of Dissolved Oxygen Across all MOATS")

SatDOplot


```



#### 9.3) Creating Percent Dissoved Oxy Value - Percent DO (with assumptions)
```{r 9.3 Creating Percent Dissoved Oxy Value - Percent DO (with assumptions) }
# Back calculated fraction DO as reported by the oxygen sensor

H2Ochemdf$percentDOassumpt <- ""
H2Ochemdf$percentDOassumpt <- as.numeric(H2Ochemdf$percentDOassumpt)
H2Ochemdf$percentDOassumpt <- H2Ochemdf$DO / H2Ochemdf$assumedSatDOmg


p5 <- ggplot(H2Ochemdf, aes(x=dateTime, y=percentDOassumpt)) +
  geom_point(aes(colour=period, point=))   +
  ggtitle("Assumed Percent DO (All Treatments & All MOATs) Colored by Period")

p5
```



#### 9.3a Filtering to Display ramp DO activity
```{r 9.3a Filtering to display ramp DO activity}

f.H2Ochemdf.ramp = filter(H2Ochemdf,
  !moats %in% c('M03', "M04", "M05", "M11") & 
  treatment %in% c("current", "allchange", "hightemperature") &
  period != "night")

f.H2Ochemdf.ramp$moats <- droplevels(f.H2Ochemdf.ramp$moats)
f.H2Ochemdf.ramp$treatment <- factor(f.H2Ochemdf.ramp$treatment)


p5 <- ggplot(f.H2Ochemdf.ramp, aes(x=dateTime, y=percentDOassumpt)) +
  geom_point(aes(colour=period, point=))   +
  facet_wrap(~treatment)
  ggtitle("Assumed Percent DO (All Treatments & All MOATs) Ramping Up From Day to Night")

p5



```



#### 9.5 Creating Percent Dissoved Oxy Value
```{r 9.5 Creating Percent Dissoved Oxy Value}
#*********************************
## 9.5) Creating Percent Dissoved Oxy Value - Observed Saturated DOmg (measured salinity)
#*********************************

# #satured mg/L at observed temperature and observed (not assumed) salinity
H2Ochemdf$sTemperature <- as.numeric(H2Ochemdf$sTemperature)

H2Ochemdf$obseveredSatDOmg <- oxySol(H2Ochemdf$sTemperature, H2Ochemdf$Final_PSU)
```



#### 9.6 Creating Percent Dissoved Oxy Value - Observed/Actual DO (in mg)
```{r 9.6 Creating Percent Dissoved Oxy Value - Observed/Actual DO (in mg) Saturated DOmg (measured salinity)}
#*********************************
## 9.6) Creating Percent Dissoved Oxy Value - Observed/Actual DO (in mg) Saturated DOmg (measured salinity)
#*********************************
# actual DO mg at observed temperature and salinity
H2Ochemdf$percentDO <- H2Ochemdf$DO / H2Ochemdf$assumedSatDOmg

H2Ochemdf$actualDOmg <- H2Ochemdf$percentDO * H2Ochemdf$obseveredSatDOmg


actualDOmgPLOT <- ggplot(H2Ochemdf, aes(x=dateTime, y=H2Ochemdf$actualDOmg)) +
  geom_point(aes(colour=period, point=))   +
  ggtitle("Actual DO (mg/L) (All Treatments & All MOATs) Colored by Period")

actualDOmgPLOT
```



# 10.0) Filtering Data
```{r 10.0 Filtering Data across all }
# # 10.0) Filtering Data

H2Ochemdf <- H2Ochemdf  %>% filter(!moats %in% c("M03", "M04", "M05", "M11")) %>%
  filter(sTemperature>= 5 & sTemperature<=30) %>%
  filter(treatment %in% c("current", "allchange", "hightemperature")) %>%
  filter(period != "other")


write.csv(H2Ochemdf, "2020.10.05_H2Ochemdf.csv")

```



#### 10.1 Filtering Data- dropping levels to clean graphs
```{r 10.1 Filtering Data- dropping lvls to clean graphs}
## 10.1) Filtering Data- dropping lvls to clean graphs
#*********************************


filteredFrame = filter(H2Ochemdf,
                       !moats %in% c('M03', "M04", "M05", "M11") & 
                         (aTemperature>= 5 & aTemperature<=30) &
                         treatment %in% c("current", "allchange", "hightemperature") &
                         period != "other")

#|- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - |

## 10.1a Dropping levels and factors
filteredFrame$moats <- droplevels(filteredFrame$moats)
filteredFrame$treatment <- factor(filteredFrame$treatment)


```



# 11.0) DO averages- days and nights
#### 11.1 DO averages- days and nights- DAY
```{r 11.1 DO averages- days and nights- DAY}
## 11.1 DO averages- days and nights

# Creating Values
# Day

allchgDay_DO <- subset(H2Ochemdf, 
                       period == "day" &  treatment == "allchange",
                      select = c(dateTime, actualDOmg))

curDay_DO <- subset(H2Ochemdf, 
                   period == "day" & treatment == "current",
                   select = c(dateTime, actualDOmg))

hitempDay_DO <- subset(H2Ochemdf, 
                      period == "day" & treatment == "hightemperature",
                      select = c(dateTime, actualDOmg))

```



#### 11.2 DO averages- days and nights- NIGHT
```{r  11.2 DO averages- days and nights- NIGHT}

# Creating Values
# Night
allchgNightDO <- subset(H2Ochemdf, 
                        period == "night" & treatment == "allchange",
                        select = c(dateTime, actualDOmg ))

curNightDO <- subset(H2Ochemdf, 
                     period == "night" & treatment == "current",
                     select = c(dateTime, actualDOmg ))

hitempNightDO <- subset(H2Ochemdf, 
                        period == "night" & treatment == "hightemperature",
                        select = c(dateTime, actualDOmg ))


```



#### 11.3 Review of Values
```{r 11.3 Review of Values}

# Review of values
allchgDay_DO
allchgNightDO
curDay_DO
curNightDO
hitempDay_DO
hitempNightDO

```



# 12.0) DO Day/Night Summary
#### 12.1 DO Day/Night Summary
```{r 12.1 DO Day/Night Summary}

dim(H2Ochemdf)

H2Ochemdf.daynight.summary <- H2Ochemdf %>% group_by(treatment, period) %>%
  summarize(sd = sd(actualDOmg, na.rm = TRUE), 
            mean = mean(actualDOmg, na.rm = TRUE), 
            median = median(actualDOmg, na.rm = TRUE),
            IQR = IQR(actualDOmg, na.rm = TRUE),
            n = n(), .groups= "drop_last") %>%
  
  mutate(se = sd/sqrt(n)) %>%
  mutate(ci = se*1.96)


#write.csv(H2Ochemdf.daynight.summary, "2020.09.22_H2Ochemdf_daynight_summary.csv")

```



#### 12.3 Summary Table Plots
```{r 12.3 Summary Table Plots}
# ggplot(H2Ochemdf, aes(treatment, actualDOmg)) +
#             geom_jitter(color = "grey") +
#             geom_boxplot(notch = TRUE, outlier.shape = NA, colour = "green") +
#             geom_point(data = H2Ochemdf.daynight.summary, aes(x=treatment, y=mean), size=5, color = "purple") + 
#             geom_errorbar(data = H2Ochemdf.daynight.summary, 
#                           aes(x=treatment, y=mean, ymin = mean-sd, ymax = mean+sd), 
#                           color = "blue") +
#             geom_errorbar(data = H2Ochemdf.daynight.summary,
#                           aes(x=treatment, y=mean, ymin = mean-ci, ymax = mean+ci),
#                           colour = "red") +
#             facet_wrap(~period) +
#             ggtitle("All Treatments, Actual Dissolved Oxygen (mg) Across Periods") +
#             theme_bw() 


```




 
## 13.2 Histogram plot- all moats, all treatments, all periods 

 Cdml %>% ggplot(data=.)+geom_histogram(aes(x=aTemperature), binwidth = .05) + 
                          xlim(5,30) +
                          ylim(0, 10000)
 
#|- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - |

## 13.2a Histrogram Scaled by Time Narrative 
# Section below walks how to quantify each "bin" by the observation period = 6.8minutes  

#|- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - |

## 13.2b Histogram scaled by time
#find duration of each observations in hours

durObsHours <- 6.8/60

# the count (number of  observations in each bin) is scale by time duration of each obs
# option to also include polygon
# could fix the vline to only show the value relevant for each plot
#vline could show acutal mean temperature, not just target
# each bin shows 0.2 degrees
p <- ggplot(Cdml, aes(aTemperature)) +
                  geom_histogram(aes(y=..count..*durObsHours), 
                                              binwidth = 0.2) +
                   #   geom_freqpoly(aes(y=..count..*durObs)) +
      geom_vline(xintercept = c(11,12,13,14), colour = "red") +
      facet_wrap(vars(treatment, period), ncol = 2, scales = "fixed") +
      theme_bw()
p

#just show bins < 12 hours
p + ylim(c(0,12))
 
## Conclusion- problem remains of how to show what percent of time it spent around
##             the average- not plain "stacking time". 

#|- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - |

## 13.3 Cumulative Frequency Distribution

p <- ggplot(Cdml, aes(aTemperature)) +
            stat_ecdf(aes(colour = moats)) + 
            geom_vline(xintercept = c(11,12,13,14), colour = "red") +
            facet_wrap(vars(treatment, period), ncol = 2, scales = "fixed")  +
            theme_bw()
p

#|- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - |
## 12.3a  Using a ECDF to better visualize distribution
#Compute empirical cumulative distribution : The empirical cumulative distribution 
#                                            function (ECDF) provides an alternative 
#                                            visualisation of distribution. 
#                                         Compared to other visualisations that rely 
#                                         on density (like geom_histogram()), the 
#                                         ECDF doesn't require any tuning parameters 
#                                         and handles both continuous and categorical 
#                                         variables. 
#|- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - |

## 13.3b ECDF Plot

p <-      ggplot(Cdml, aes(aTemperature)) +
                stat_ecdf(aes(colour = moats)) + 
                geom_vline(xintercept = Cdml.daynight.summary$mean, colour = "red") +
                facet_wrap(vars(treatment, period), ncol = 2, scales = "fixed")  +
                theme_bw()
p
 
#|- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - |
## 13.3c Creating a function to incorporate our statisitics- show our averages

 coolECDF <- function(d, dsum, treat, per){
   dsum <- dsum %>% filter(treatment == treat & period == per )
   p <- d %>% filter(treatment == treat & period == per ) %>% ggplot(aes(aTemperature)) +
     stat_ecdf(aes(colour = moats)) + 
     geom_vline(xintercept = dsum$mean, colour = "red") +
     ggtitle(paste(treat, per)) +
     theme_bw()
   return(p)
 }
 
#|- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - |

  levels(Cdml$treatment)
  levels(factor(Cdml$period))

#|- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - | 
## 13.3d Using the coolECDF function per treatment & period

        cfd.a.d <- coolECDF(Cdml, Cdml.daynight.summary, "allchange", "day")
        cfd.a.n <- coolECDF(Cdml, Cdml.daynight.summary, "allchange", "night")
        cfd.c.d <- coolECDF(Cdml, Cdml.daynight.summary, "current", "day")
        cfd.c.n <- coolECDF(Cdml, Cdml.daynight.summary, "current", "night")
        cfd.h.d <- coolECDF(Cdml, Cdml.daynight.summary, "hightemperature", "day")
        cfd.h.n <- coolECDF(Cdml, Cdml.daynight.summary, "hightemperature", "night")
 
#|- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - |
## 13.4 Incorporating Grid Arrange to display the ECDF plots        
# Basic Grid Arrange

      grid.arrange(cfd.a.d, cfd.c.d, cfd.h.d, nrow = 1)
 
      grid.arrange(cfd.a.n, cfd.c.n, cfd.h.n, nrow = 1) 
      
      #make a list of all the plots then pass the list to grid.arrange()
      ecdfList <- list(cfd.a.d, cfd.c.d, cfd.h.d, cfd.a.n, cfd.c.n, cfd.h.n)
      grid.arrange(grobs = ecdfList, ncol=3)
      
      
 

#|- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - |
## 13.5 Investigating tails
#to look a little more closely at the tails
#lower 1% 
      
lowerTail <- function(p){
  return(p + ylim(c(0,0.01)))
}

upperTail <- function(p){
  return(p + ylim(c(0.99,1.0)))
}

lowerP <- lapply(ecdfList, lowerTail)
grid.arrange(grobs = lowerP, ncol=3)

upperP <- lapply(ecdfList, upperTail)
grid.arrange(grobs = upperP, ncol=3) 

 # p + ylim(c(0,0.01))
 # #upper 1%
 # p + ylim(c(0.99,1))
 # 
 # #to look a little more closely at the tails
 # #lower 1% 
 # cfd.a.d + ylim(c(0,0.01))
 # #upper 1%
 # p + ylim(c(0.99,1))

#|- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - | 
## 13.6 Plain time series
# example plot

 ggplot(subset(Cdml[Cdml$treatment == "allchange", ], 
               period %in% ("night")), 
        aes(x=dateTime, y=aTemperature)) + 
        geom_point(aes(colour=moats, point=)) + 
        ylim (10, 16) 
 
#|- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - |  
## 13.7 Violin Plot 
# example plot
 p_allchg_d_facet_violin <- ggplot(subset(Cdml[Cdml$treatment == "allchange", ]), 
                                   aes(x=moats, y=aTemperature, colour=moats)) + 
                            geom_hline(yintercept = avg_allchgDayaTemp) +
                            geom_jitter(shape=16, position=position_jitter(0.2), 
                                  color="light grey") + 
                            geom_hline(yintercept = avg_allchgNightaTemp) +
                            geom_violin(aes(colour = period)) +
                            stat_summary(fun=mean, geom="point", size=1, color="purple")  + 
                            facet_grid(period~moats) 
 
 p_allchg_d_facet_violin
#|- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - |  
# 13.7a faceted violin plot

 p_allchg_d_facet_violin <- ggplot(subset(Cdml[Cdml$treatment == "allchange", ]), 
                                   aes(x=moats, y=aTemperature, colour=moats)) + 
                            geom_hline(yintercept = avg_allchgDayaTemp) +
                            geom_jitter(shape=16, position=position_jitter(0.2), 
                                  color="light grey") + 
                            geom_hline(yintercept = avg_allchgNightaTemp) +
                            geom_violin(aes(colour = period)) +
                            geom_boxplot() +
                            stat_summary(fun=mean, geom="point", size=1, color="purple")  + 
                            facet_grid(period~moats) 
 
 
 p_allchg_d_facet_violin
#|- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - | 
## 13.7b Simple violin plot
# note that day and night are not filtered
vp <-    ggplot(filteredFrame, 
                aes(x=filteredFrame$aTemperature, 
                y=filteredFrame$treatment)) + 
        geom_violin() 

vp

#display the plot
vp

# Rotate the violin plot
vp + coord_flip()
 
#|- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - |  
## 13.7c Simple violin plot with ggplot, filtered day and night

p_allchg_n <- ggplot(subset(Cdml[Cdml$treatment == "allchange", ], 
                            period %in% ("night")), 
                            aes(x=moats, y=aTemperature, colour=treatment)) + 
              stat_summary(fun=mean, geom="point", size=2, color="red")  + 
              geom_jitter(shape=16, position=position_jitter(0.2), 
                            color="blue") + 
              geom_hline(yintercept = 13.9) +
              geom_violin() +
              geom_boxplot(width= 0.1) +
  
              ggtitle("Day Period - All Change Treatment")


#display the plot
p_allchg_n

#|- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - | 

## 13.7c Simple violin plot, filtered day and night, jitter points for Temp Jumps
p_allchg_d_jitter <- ggplot(subset(Cdml[Cdml$treatment == "allchange", ], 
                                   period %in% ("day")), 
                            aes(x=moats, y=aTemperature, colour=treatment)) + 
                     stat_summary(fun=mean, geom="point", size=2, color="red")  + 
                    geom_jitter(aes(colour = tDeltaThreshold)) +
                    geom_hline(yintercept = avg_allchgDayaTemp) +
                    geom_boxplot() +
                    ggtitle("Day Period - All Change Treatment- Temp Jumps (.5C)")


#display the plot
p_allchg_d_jitter

#|- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - | 




 
#*********************************
 ## 14.) aTemp bands investig.
#*********************************

 
#|- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - | 
# Selecting for the high aTemperature Band
 investig.HighaTemp <- Cdml %>% 
   filter(aTemperature>= 14.50 & aTemperature<=15.50) %>%
   filter(treatment %in% c("current", 
                           "allchange", 
                           "hightemperature")) %>%
   filter(period != "other")

#|- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - |  
 # Time series plot 
 ggplot(subset(investig.HighaTemp[investig.HighaTemp$treatment == "current", ], 
               period %in% ("night")), 
        aes(x=dateTime, y=aTemperature)) + 
   geom_point(aes(colour=moats, point=)) +
   ylim (10, 20)
 
#|- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - | 
 # Selecting for the high aTemperature Band
 investig.LowaTemp <- scrubdml %>% 
   filter(aTemperature>= 10.50 & aTemperature<=11.50) %>%
   filter(treatment %in% c("current", 
                           "allchange", 
                           "hightemperature", 
                           "ambient_M04", 
                           "ambient_M05")) %>%
   filter(period != "other")
 
 #|- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - | 

ggplot(subset(Cdml[Cdml$treatment == "hightemperature", ],
              period %in% ("day")), 
              aes(x=dateTime, y=aTemperature)) + 
              geom_point(aes(colour=moats)) + 
              ylim (10, 16)
 
#|- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - | 

p_cur_night_investig <- ggplot(subset(investig.HighaTemp[investig.HighaTemp$treatment == "current", ], 
                                       period %in% ("night")), 
                                aes(x=moats, y=aTemperature, colour=treatment)) + 
   geom_boxplot() +
   geom_boxplot(data= scrubdml, x=moats, y=aTemperature) +
   ggtitle("CurrentTreatment, Night Period")

p_cur_night_investig 

 
#|- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - | 
 
 # Time series plot 
 ggplot(subset(investig.LowaTemp[investig.LowaTemp$treatment == "hightemperature", ], 
               period %in% ("night")), 
        aes(x=dateTime, y=aTemperature)) + 
   geom_point(aes(colour=moats, point=)) +
   ylim (9, 12.5)
 
#|- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - | 
 
 









# 13.0 Timeseries for the Winter Storm Event
Major rainfall event at Mukilteo on 18OCT20 into 19OCT20. 
Sediment from run off clogged filters. Slowed water input cycle. 
Bubble Box, local MOATs reservoir ran dry. Heating element in some bubble boxes melted incoming gas exchange lines. 
Effects to water temperature and chemistry lasted into 20OCT20 and beyond in some cases.



#### 13.1 All Change MOATS Winter Storm "Reactions"
```{r 13.1.1 Aquarium Temperature All Change Conditions Treatment Replicates' Reaction to Winter Storm}

#aTemp Plot

WNTR.STRM_Allchg_aTempPlot <- ggplot(subset(H2Ochemdf, 
               treatment %in% ("allchange")), 
        aes(x=ObservationDate, y=aTemperature)) + 
        geom_point(aes(colour=moats, point=)) +
        facet_wrap(~period) +
        ggtitle("Aquarium Temperature All Change Conditions Treatment Replicates' Reaction to Winter Storm")
WNTR.STRM_Allchg_aTempPlot

```
We see loss in temperature control between 18OCT20-20OCT20. 



```{r 13.1.2 Dissovled Oxygen All Change Conditions Treatment Replicates' Reaction to Winter Storm}

#DO Plot

WNTR.STRM_Allchg_DO.Plot <- ggplot(subset(H2Ochemdf, 
               treatment %in% ("allchange")), 
        aes(x=ObservationDate, y=actualDOmg)) + 
        geom_point(aes(colour=moats, point=)) +
        facet_wrap(~period)
        ggtitle("Dissovled Oxygen All Change Conditions Treatment Replicates' Reaction to Winter Storm")
WNTR.STRM_Allchg_DO.Plot

```


```{r 13.1.2 Dissovled Oxygen All Change Conditions Treatment Replicates' Reaction to Winter Storm}

#DO Plot

WNTR.STRM_Allchg_DO.Plot <- ggplot(subset(H2Ochemdf, 
               treatment %in% ("allchange")), 
        aes(x=ObservationDate, y=percentDO)) + 
        geom_point(aes(colour=moats, point=)) +
        facet_wrap(~period)
        ggtitle("Dissovled Oxygen (percentage) All Change Conditions Treatment Replicates' Reaction to Winter Storm")
WNTR.STRM_Allchg_DO.Plot

```


MOATs 02 and 13 struggle to maintain 60% DO treatment from 19OCT20 onwards.  


```{r 13.1.3 pH All Change Conditions Treatment Replicates' Reaction to Winter Storm}

#pH Plot

WNTR.STRM_Allchg_pH.Plot <- ggplot(subset(H2Ochemdf, 
               treatment %in% ("allchange")), 
        aes(x=ObservationDate, y=pH)) + 
        geom_point(aes(colour=moats, point=)) +
        facet_wrap(~period)
        ggtitle("pH All Change Conditions Treatment Replicates' Reaction to Winter Storm")
WNTR.STRM_Allchg_pH.Plot

```
 

Peaks in pH during the day time period are likely explained by degraded elements following the 18OCT19 winter storm. 



#### 13.2 Current Treatments MOATS Winter Storm "Reactions"

```{r 13.2.1 Aquarium Temperature Current Conditions Treatment Replicates' Reaction to Winter Storm}

#aTemp Plot

WNTR.STRM_cur_aTempPlot <- ggplot(subset(H2Ochemdf, 
               treatment %in% ("current")), 
        aes(x=ObservationDate, y=aTemperature)) + 
        geom_point(aes(colour=moats, point=)) +
        facet_wrap(~period) +
        ggtitle("Aquarium Temperature Current Conditions Treatment Replicates' Reaction to Winter Storm")
WNTR.STRM_cur_aTempPlot

```

We see loss in temperature control following 18OCT20-20OCT20, in particular MOATs 07.  


```{r 13.2.2 Dissovled Oxygen Current Conditions Treatment Replicates' Reaction to Winter Storm}

#DO Plot

WNTR.STRM_cur_DO.Plot <- ggplot(subset(H2Ochemdf, 
               treatment %in% ("current")), 
        aes(x=ObservationDate, y=actualDOmg)) + 
        geom_point(aes(colour=moats, point=)) +
        facet_wrap(~period)
        ggtitle("Dissovled Oxygen Current Conditions Treatment Replicates' Reaction to Winter Storm")
WNTR.STRM_cur_DO.Plot

```


```{r 13.2.2a Dissovled Oxygen Current Conditions Treatment Replicates' Reaction to Winter Storm}

#DO Plot

WNTR.STRM_cur_DO.Plot <- ggplot(subset(H2Ochemdf, 
               treatment %in% ("current")), 
        aes(x=ObservationDate, y=percentDO)) + 
        geom_point(aes(colour=moats, point=)) +
        facet_wrap(~period)
        ggtitle("Dissovled Oxygen (percentage) Current Conditions Treatment Replicates' Reaction to Winter Storm")
WNTR.STRM_cur_DO.Plot

```


MOATs 07 struggle to maintain 60% DO treatment from 19OCT20 onwards.  


#### 13.3 High Temperature MOATS Winter Storm "Reactions"


```{r 13.3.1 pH Current Conditions Treatment Replicates' Reaction to Winter Storm}

#pH Plot

WNTR.STRM_hightemp_pH.Plot <- ggplot(subset(H2Ochemdf, 
               treatment %in% ("hightemperature")), 
        aes(x=ObservationDate, y=pH)) + 
        geom_point(aes(colour=moats, point=)) +
        facet_wrap(~period) +
        ggtitle("pH Current Conditions Treatment Replicates' Reaction to Winter Storm")
WNTR.STRM_hightemp_pH.Plot

```

MOATs 07 and MOATs 10 endured pH problems around the winter storm events.  



```{r 13.3.3 Dissovled Oxygen High Temperature Conditions Treatment Replicates' Reaction to Winter Storm}

#DO Plot

WNTR.STRM_hightemp_DO.Plot <- ggplot(subset(H2Ochemdf, 
               treatment %in% ("hightemperature")), 
        aes(x=ObservationDate, y=actualDOmg)) + 
        geom_point(aes(colour=moats, point=)) +
        facet_wrap(~period)
        ggtitle("Dissovled Oxygen High Temperature Conditions Treatment Replicates' Reaction to Winter Storm")
WNTR.STRM_hightemp_DO.Plot

```


```{r 13.3.2a Dissovled Oxygen Current Conditions Treatment Replicates' Reaction to Winter Storm}

#DO Plot

WNTR.STRM_hightemp_DO.Plot <- ggplot(subset(H2Ochemdf, 
               treatment %in% ("hightemperature")), 
        aes(x=ObservationDate, y=percentDO)) + 
        geom_point(aes(colour=moats, point=)) +
        facet_wrap(~period)
        ggtitle("Dissovled Oxygen (percentage) High Temperature Conditions Treatment Replicates' Reaction to Winter Storm")
WNTR.STRM_hightemp_DO.Plot

```



```{r 13.3.3 pH High Temperature Conditions Treatment Replicates' Reaction to Winter Storm}

#pH Plot

WNTR.STRM_hightemp_pH.Plot <- ggplot(subset(H2Ochemdf, 
               treatment %in% ("hightemperature")), 
        aes(x=ObservationDate, y=pH)) + 
        geom_point(aes(colour=moats, point=)) +
        facet_wrap(~period) +
        ggtitle("pH Current Conditions Treatment Replicates' Reaction to Winter Storm")
WNTR.STRM_hightemp_pH.Plot

```





.**************E*N*D*************# 
.*********************************
.# END OF SCRIPT | END OF DOCUMENT 
.*********************************


. ___________________8888,
. ____________________Y8888b,
. ___________________,oA8888888b,
. _____________,aaad8888888888888888bo,
. __________,d888888888888888888888888888b,
. ________,888888888888888888888888888888888b,
. _______d8888888888888888888888888888888888888,
. ______d888888888888888888888888888888888888888b
. _____d888888P'                    `Y888888888888,
. _____88888P'                    Ybaaaa8888888888l
. ___a8888'                      `Y8888P' `V888888
. __d8888888a                                `Y8888
. AY/'' `\Y8b                                 ``Y8b
. Y'      `YP                                    ~~